---
title: "Homework1"
output: github_document
date: "2026-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```
In this dataset, the species are `r paste(levels(penguins$species), collapse = ", ")`, and the islands are `r paste(levels(penguins$island), collapse = ", ")`.And each row represents one penguin. Other variables are `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year`. 

The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables.

The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 1)` mm

```{r penguins_scatterplot}
library(ggplot2)

penguins_scatterplot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

penguins_scatterplot
ggsave("penguins_scatterplot.pdf", plot = penguins_scatterplot, height = 4, width = 6)
```
#Problem2

```{r problem2}
set.seed(1234)
random_sample <- rnorm(10)
random_sample

is_positive <- random_sample > 0
is_positive

characters <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j")
characters

category <- factor(c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A"))
category

library(tidyverse)

problem2_df = tibble(
  random_sample = random_sample,
  is_positive = is_positive,
  characters = characters,
  category = category
)
problem2_df
```
```{r problem2-means}
mean(pull(problem2_df, random_sample))
mean(pull(problem2_df, is_positive))
mean(pull(problem2_df, characters))
mean(pull(problem2_df, category))

```
The mean only works for `random_sample` and `is_positive`, it only works for numerical and logical variables.The mean does not work for `characters` and `category`.Because character and factor variables cannot be averaged directly.

```{r problem2-conversion, results='hide', warning=FALSE}
as.numeric(pull(problem2_df, is_positive))
as.numeric(pull(problem2_df, characters))
as.numeric(pull(problem2_df, category))
```
as.numeric() turns TRUE into 1 and FALSE into 0, which can explain why the logical variable has a mean of 0.4.
The letters become NA because they are not numbers. 
The factor values become 1, 2 and 3, but these are just representation for A, B, and C, so their average would not be meaningful.
